---
title: "Confirmatory Factor Analysis"
author: "Mohd Azmi"
date: "18/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment

## Library

```{r}
library(pacman)
p_load(tidyverse, haven, summarytools, psych, MVN, lavaan, semTools, semPlot)
```


## Dataset

```{r}
analds0 <- read_sav("exercise motivation.sav")
analds <- analds0 %>% mutate_if(is.labelled, ~(as_factor(.))) %>% print()
```

# Analysis

## Step 1: Exploration

```{r}
descr(analds)
```


## Step 2: Normality

```{r}
analds_score <- analds %>% select(-ID, -gender) %>% print()

mardia_score <- mvn(analds_score, mvnTest = "mardia", multivariatePlot = "qq") %>% print()

mardia(analds_score, plot = T)
```


## Step 3 - Specify the measurement model

```{r}
model1 = "
mastery =~ M1 + M2 + M3 + M4
enjoy =~ E1 + E2 +E3"

cfa_model1 <- cfa(model1, data=analds_score, estimator = "MLR")
summary(cfa_model1, fit.measures = T, standardized = T)
```

CFI = 0.984
- read at robust column

TLI = 0.975

SRMR = 0.049

RMSEA = 0.050
(90% CI) = 0.000, 0.086
CIfit = 0.456


## Step 4 - Assessing Measurement Model Validity

Standardized factor loading - refer latent variables in above - see column std. all, or refer sem plot below

```{r}
sr_model1 <- residuals(cfa_model1, type = "Standardized") %>% print()
mi_model1 <- modificationIndices(cfa_model1)
mi_model1
#subset(mi_model1, mi.scaled > 3.84)
```


## Step 5 - Composite Reliability

```{r}
reliability(cfa_model1)
reliability(cfa_model1)[2,]
```

read on omega reading

composite reliability : `r reliability(cfa_model1)[2,]`

## Plot

```{r}
semPaths(cfa_model1, what = "path", whatLabels = "std", style = "lisrel", edge.color = "black", intercepts = F)
```


