---
title: "Factor Analysis Practical"
author: "Mohd Azmi"
date: "25/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prelim - EFA

## Libraries

```{r}
library(pacman)
p_load(haven, tidyverse, psych, lattice, summarytools, broom)
```

## Dataset

```{r}
myds0 <- read_sav("Attitude_Statistics v3.sav") %>% #import
  zap_labels() %>%  #removed spss label
  select(-ID) #removed ID
myds0
```

# Analysis - EFA

## Descriptive & Exploration

```{r}
myds0 %>% descr()
```

## Normality

### Histogram

```{r}
ggplot(gather(myds0), aes(x=value, y=(..count../sum(..count..))*1000)) +
  geom_bar() + ylab("Percent") + xlab("Score") +
  facet_wrap(~key)
```

### Shapiro Wilk Test

```{r}
mapply(shapiro.test, myds0)
```

### Multivariate Normality

```{r}
mardia(myds0)
```

## Step1

### KMO MSA

```{r}
KMO(myds0)
```

### Bartlet Test of sphericity

```{r}
cortest.bartlett(myds0)
```

### Eigenvalues and scree plot

```{r}
scree_plot0 <- scree(myds0)
scree_plot0
```

### Parallel Analysis

```{r}
parallel_myds0 <- fa.parallel(myds0, fm = "pa", fa = "fa")
parallel_myds0
```

### VSS

```{r}
vss(myds0)
```

## Step 2

### EFA

```{r}
efa_myds0 <- fa(myds0, nfactors = 2, fm = "pa", rotate = "oblimin")
print(efa_myds0, cut = .3, digits = 3)
```

```{r}
print(efa_myds0, digits = 3)
```

## Step 3

### remove Q1

```{r}
efa_myds_m1 <- fa(subset(myds0, select = -Q1), nfactors = 2, fm = "pa", rotate = "oblimin")
print(efa_myds_m1, cut = .3, digits = 3)
```

### remove Q12

```{r}
efa_myds_m2 <- fa(subset(myds0, select = -c(Q1,Q12)), nfactors = 2, fm = "pa", rotate = "oblimin")
print(efa_myds_m2, cut = .3, digits = 3)
```

### Remove Q2

```{r}
efa_myds_m3 <- fa(subset(myds0, select = -c(Q1,Q3, Q12)), nfactors = 2, fm = "pa", rotate = "oblimin")
print(efa_myds_m3, cut = .3, digits = 3)
```

### Remove Q3

```{r}
efa_myds_m4 <- fa(subset(myds0, select = -c(Q1,Q2, Q3, Q12)), nfactors = 2, fm = "pa", rotate = "oblimin")
print(efa_myds_m4, cut = .3, digits = 3)
```

## Summary

1. PA1: Q4, Q5, Q6, Q7, Q11
2. PA2: Q8, Q9, Q10

## Cronbach Alpha - Internal Consistency Reliability

```{r}
PA1 <- c("Q4", "Q5", "Q6", "Q7", "Q11")
PA2 <- c("Q8", "Q9", "Q10")
```


### PA1

```{r}
ca_PA1 <- alpha(myds0[PA1])
print(ca_PA1, digits = 3)
```


### PA2

```{r}
ca_PA2 <- alpha(myds0[PA2])
print(ca_PA2, digits = 3)
```


# Prelim - CFA

## Libraries

```{r}
p_load(lavaan, semTools, semPlot)
```

## Dataset

take 

1. PA1: Q4, Q5, Q6, Q7, Q11
2. PA2: Q8, Q9, Q10

```{r}
mydsCFA0 <- myds0 %>% select("Q4", "Q5", "Q6", "Q7", "Q11", "Q8", "Q9", "Q10")
mydsCFA0
```

# Analysis - CFA

## Descriptive & Exploratory

### Descriptive

```{r}
mydsCFA0 %>% descr()
```

### Normality

```{r}
mardia(mydsCFA0)
```

## Step 1 - Specify Measurement Model

```{r}
model <- "
PA1 =~ Q4 + Q5 + Q6 + Q7 + Q11
PA2 =~ Q8 + Q9 + Q10
"
```

## Step 2 - Fit the model

```{r}
cfa_mod0 <- cfa(model, data = mydsCFA0, estimator = "MLR")
summary(cfa_mod0, fit.measures = T, standardized = T)
```

```{r}
standardizedSolution(cfa_mod0)
```

```{r}
mod_index_cfamod0 <- modificationIndices(cfa_mod0)
subset(mod_index_cfamod0, mod_index_cfamod0 > 3.84)
```

```{r}
stdresid_cfamod0 <- residuals(cfa_mod0, type = "standardized")
stdresid_cfamod0
```

# SEM Path

```{r}
semPaths(cfa_mod0, "path", "std", style = "lisrel")
```

